Listings of equations, figures, tables and sections of the article '{\it \bf Musical elements in the discrete-time representation of sound}' and of the scripts in the MASS toolbox

### 2017-08-05 article/acm/body.tex
finished the listings
added a section on synonymy and polysemy and other minor improvements

The reminder of this article is organized as follows:
Section~\ref{sec:discNote} characterizes the basic musical note;
Section~\ref{sec:internalVar} develops internal dynamics of musical notes;
Section~\ref{sec:notesMusic} tackles the organization of musical notes in
higher level musical structures~\cite{Wisnick,Webern,Lerdahl,Cook,Lacerda,Zamacois,Schoenberg,microsound}.
As these descriptions require knowledge on topics such as psychoacoustics, cultural traditions,
and mathematical formalisms, the text points to external complements as needed
and presents methods, results and discussions altogether.
Section~\ref{cap:conclusao} holds final considerations and further work.
The Supporting Information document~\cite{SI} holds an informative listing of all the equations, figures, tables and sections in this document
and the scripts in the \massa\ toolbox\footnote{The toolbox contains a collection of Python scripts which:
\begin{itemize}
    \item implement each of the equations;
    \item render music and illustrate the concepts;
    \item render each of the figures used in this article.
\end{itemize}
Additionally, the documentation of the toolbox consists of this article and the scripts themselves.}.

@@

\begin{figure}[h!]
    {\centering
        \includegraphics[width=.5\columnwidth]{figures/mixagem__}}
    \caption{Mixing of three sound sequences. The amplitudes are directly summed.}
        \label{fig:mixagem}
\end{figure}

@@

\subsubsection{Moving source and receptor, Doppler effect}
According to the description in Section~\ref{subsec:spac}, when an audio source or receptor is moving, its characteristics are ideally updated at each sample of the digital signal (if fast computational rendering is not at stake). Velocity components should be found for each ear. Hence, given the audio source velocity $v_s$, with positive values if the source moves away from receptor, and receptor velocity $v_r$, positive when it gets closer to audio source, the frequency is given by the well-known shift in the Doppler effect:

\begin{equation}\label{eq:fDoppler}
    f=\left(\frac{v_{sound}+v_r}{v_{sound}+v_s}\right)f_0
\end{equation}

>>>>

The reminder of this article is organized as follows:
Section~\ref{sec:discNote} characterizes the basic musical note;
Section~\ref{sec:internalVar} develops internal dynamics of musical notes;
Section~\ref{sec:notesMusic} tackles the organization of musical notes in
higher level musical structures~\cite{Wisnick,Webern,Lerdahl,Cook,Lacerda,Zamacois,Schoenberg,microsound}.
As these descriptions require knowledge on topics such as psychoacoustics, cultural traditions,
and mathematical formalisms, the text points to external complements as needed
and presents methods, results and discussions altogether.
Section~\ref{cap:conclusao} holds final considerations and further work.

\subsection{Additional material}
The Supporting Information document~\cite{SI} holds commented listings of all the equations, figures, tables and sections in this document
and the scripts in the \massa\ toolbox\footnote{The toolbox contains a collection of Python scripts which:
\begin{itemize}
    \item implement each of the equations;
    \item render music and illustrate the concepts;
    \item render each of the figures used in this article.
\end{itemize}
Additionally, the documentation of the toolbox consists of this article and the scripts themselves.}.
The musical pieces are not very traditional which facilitates the understanding of specific techniques
and the extrapolation of the note concept.

\subsection{Synonymy and polysemy (disclaimer)}
Given that the main topic of this article (the expression of musical elements
in PCM audio) is multidisciplinary and involves art,
the reader should be aware that many of the vocabulary admit different choices of terms and definitions.
More specifically, it is often often the case where many words can express the same concept
and where one word can carry different meanings.
This is a very deep issue which might receive a dedicated manuscript.
The reader might need to read the rest of this document to understand this
small selection of synonymy and polysemy in the literature,
but it is important to illustrate the point before the more dense sections:
\begin{itemize}
	\item A ``note'' can mean a pitch or an abstract construct with pitch and duration or a sound emitted from a musical instrument or a specific note in a score or a music.
	\item The sampling rate (discussed above) is also called the sampling frequency.
	\item An harmonic in a sound is most often a sinusoidal component which is is the harmonic series of the fundamental frequency. Many times, however, the terms harmonic and component are not distinguished. A harmonic can also be a note performed in a instrument by preventing certain overtones (components).
	\item Harmony can refer to chords or to note sets related to chords or even to ``harmony'' in a more general sense, as a kind of balance and consistency.
	\item A ``tremolo'' can mean different things, e.g. in a piano score, a tremolo is a fast alternation of two notes (pitches) while in computer music theory it is (most often) an oscillation of intensity.
\end{itemize}

We strived to avoid nomenclature clashes and the use of more terms and needed.
Also, some of these issues are exposed when the context is convenient, such as in the discussion of timbre.

@@

\begin{figure}[h!]
    {\centering
        \includegraphics[width=.5\columnwidth]{figures/mixagem__}}
    \caption{Mixing of three sound sequences. The amplitudes are directly summed sample-by-sample.}
        \label{fig:mixagem}
\end{figure}

@@

\subsubsection{Moving source and receptor, Doppler effect}
According to the description in Section~\ref{subsec:spac}, when an audio source or receptor is moving, its characteristics are ideally updated at each sample of the digital signal (if fast computational rendering is not at stake). Velocity components should be found for each ear. Hence, given the audio source speed $s_s$, with positive values if the source moves away from receptor, and receptor speed $s_r$, positive when it gets closer to audio source, the frequency is given by the well-known shift in the Doppler effect:

\begin{equation}\label{eq:fDoppler}
    f=\left(\frac{s_{sound}+s_r}{s_{sound}+s_s}\right)f_0
\end{equation}
